---
title: "Sphericity Tests"
author: "Van Thuan Romoli"
output: pdf_document
header-includes:
- \usepackage{amsmath}
date: "2024-10-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(MASS)
library(mixtools)
library(matrixcalc)
library(car)
inc <- function(x) {
 eval.parent(substitute(x <- x + 1))
}
```

# Statistics

Below is the code to calculate the statistic $u$ and $u'$.

```{r}
u0 <- function(data) {
  # sample covariance matrix
  S <- cov(data)
  # number of variables
  p <- ncol(data)
  # number of observations
  n <- nrow(data)
  
  u <-p^p * det(S) / (sum(diag(S)))^p
  return(-n* log(u))
}

u1 <- function(data) {
# sample covariance matrix
  S <- cov(data)
# number of variables
  p <- ncol(data)
# u and statistic u'
  u <-p^p * det(S) / (sum(diag(S)))^p
# number of observations
  n <- nrow(data)
  
  u1 <- -(n-1 - ((2* p^2 +p +2)/( 6* p))) * log(u)
  return(u1)
}
```


# Sphericity test
A function to carry out the hypothesis test, such that if $u' > \chi^2_{\alpha;\nu}$, then $u'$ lands in the critical region and we reject $H_0$.

```{r}
sphertestu0 <- function(data,alpha = 0.05) {
  u0 <- u0(data)
  p <- ncol(data)
  df <- 1/2 * p * (p+1) -1
  quantile <- qchisq(1-alpha,df)

  if (u0 > quantile) {
    return(paste("Using the u0 statistic, we reject the null hypothesis at the",alpha,"signifcance level; that is, we reject the sphericity hypothesis. The test statistic is",round(u0,2),"and the critical value is",round(quantile,2)))
  } else {
    return(paste("Using the u0 statistic, we do not reject the null hypothesis at the",alpha,"significance level; that is, we do not reject the sphericity hypothesis. The test statistic is",round(u0,2),"and the critical value is",round(quantile,2)))
  }
}

sphertestu1 <- function(data,alpha = 0.05) {
  u1 <- u1(data)
  p <- ncol(data)
  df <- 1/2 * p * (p+1) -1
  quantile <- qchisq(1-alpha,df)

  if (u1 > quantile) {
    return(paste("Using the u1 statistic, we reject the null hypothesis at the",alpha,"signifcance level; that is, we reject the sphericity hypothesis. The test statistic is",round(u1,2),"and the critical value is",round(quantile,2)))
  } else {
    return(paste("Using the u1 statistic, we do not reject the null hypothesis at the",alpha,"significance level; that is, we do not reject the sphericity hypothesis. The test statistic is",round(u1,2),"and the critical value is",round(quantile,2)))
  }
}
```


## Example (real data set)
We now illustrate the above with the following example.

Timm (1975) reported the result of an experiment in which subjects responded to "probe words" at five positions in a sentence. The variables are response times for the $j$th probe word, $y_j$, for $j = 1,2,...,5$.

```{r}
y1 <- c(51,27,37,42,27,43,41,38,36,26,29)
y2 <- c(36,20,22,36,18,32,22,21,23,31,20)
y3 <- c(50,26,41,32,33,43,36,31,27,31,25)
y4 <- c(35,17,37,34,14,35,25,20,25,32,26)
y5 <- c(42,27,30,27,29,40,38,16,28,36,25)
response.time <- data.frame(y1,y2,y3,y4,y5)
response.time
```

We would expect the variables to be correlated, and to check, we run our sphericity test.

```{r}
sphertestu0(response.time)
sphertestu1(response.time)
```

As expected, we reject the null hypothesis that the positions of the word at which the participants responded are independent.


## Example (simulated data set)


```{r}
# Test by simulating a bivariate normal distribution
N <- 1000 # Number of random samples
# set.seed(123)
# Target parameters for univariate normal distributions
rho <- 0
mu1 <- 0; s1 <- 1
mu2 <- 0; s2 <- 1

# Parameters for bivariate normal distribution
mu <- c(mu1,mu2) # Mean
sigma <- matrix(c(s1^2, s1*s2*rho, s1*s2*rho, s2^2),
           2) # Covariance matrix

# Function to draw ellipse for bivariate normal data
ellipse_bvn <- function(bvn, alpha){
  Xbar <- apply(bvn,2,mean)
  S <- cov(bvn)
  ellipse(Xbar, S, alpha = alpha, col="red")
}

bvn1 <- mvrnorm(N, mu = mu, Sigma = sigma ) # from MASS package
colnames(bvn1) <- c("bvn1_X1","bvn1_X2")

par(pty="s")
plot(bvn1,xlab="X1",ylab="X2",main = "Bivariate normal plot")
#ellipse_bvn(bvn1,0.1)

sphertestu0(bvn1,0.05)
sphertestu1(bvn1,0.05)

```


# Challenge 1: Approximate distribution

## simulation
Evaluating the approximate distribution of -n log u and u'

```{r}
u0_distr_n <- list()
u0_alpha_n <- list()

u1_distr_n <- list()
u1_alpha_n <- list()
k = 1

num_of_obs <- seq(from=11,to=21,by=2)


for(N in num_of_obs) {
  nboot <- 10000 # Number of bootstraps
  alpha <- 0.05 # Significance level
  P <- 10 # Number of variables
  degfreed <- 1/2 * P * (P+1) -1 #degrees of freedom

  # Parameters for multivariate normal distribution, under H0.
  mu <- rep(0,P) # Mean vector
  sigma <- diag(P) # Covariance matrix

  u0_distr <- rep(0,nboot)
  u1_distr <- rep(0,nboot)

  for (i in 1:nboot) {
    mvn <- mvrnorm(N, mu = mu, Sigma = sigma ) # from MASS package
    u0_distr[i] <- u0(mvn)
    u1_distr[i] <- u1(mvn)

  }
  
  u0_distr_n[[k]] <-  u0_distr
  u0_alpha_n[[k]] <- (length(which(u0_distr_n[[k]] > qchisq(1-alpha,degfreed)))) / length(u0_distr_n[[k]])
  u1_distr_n[[k]] <-  u1_distr
  u1_alpha_n[[k]] <- (length(which(u1_distr_n[[k]] > qchisq(1-alpha,degfreed)))) / length(u1_distr_n[[k]])

  inc(k)
}
```

## plots u

```{r}
index = 2

# Defines the parameters of the plot
x.grid <- seq(0,120,length = 10000)
chisqcurve <- dchisq(x.grid, df = degfreed)


# Histogram of the distribution of u0 for one specific population size, overlapped by theoretical curve
par(pty="s")
hist(u0_distr_n[[index]], prob = TRUE, col = "white", ylim = c(0, max(chisqcurve)), breaks = 50);lines(x.grid, chisqcurve, col = 2, lwd = 2)
# Produces a Q-Q plot
theoretical_u0 <- qchisq(ppoints(length(u0_distr_n[[index]])), df = degfreed)
qqplot(theoretical_u0,u0_distr_n[[index]]);abline(a= 0, b=1)
# use "xlim = c(0,40), ylim=c(0,40)" as arguents of "qqplot" to zoom into the tails of the qq plot

# Plot of the distribution of u0 approaching the chi-sq distribution as n increases
par(cex.axis=1.5,cex.lab =1.5)
plot(x.grid,chisqcurve, type = 'l', main = "",lwd = 2, xlab="U", ylab="density",ylim = c(0,0.04), xlim = c(20,110))
for (i in 1:length(u0_distr_n)) {
  lines(density(u0_distr_n[[i]]),col = i+1,lwd = 2)
  #legend("topright", col = 1:7, legend = c("chi-sq","n=11","n=13","n=15","n=17","n=19","n=21"),lty=1)
}

# Plots the distance from the chi-sq distribution
u0_distance <- list()
for (i in 1:length(u0_distr_n)){
  u0_distance[[i]] <- sum(abs(quantile(density(u0_distr_n[[i]])$x,seq(0,0.99,0.01))-qchisq(seq(0,0.99,0.01),degfreed)))/100
}
plot(num_of_obs,u0_distance,type = "o",ylim=c(0,15000))


# Plots the value alpha as n increases
plot(num_of_obs,u0_alpha_n, type = "o");abline(h = 0.05)

plot(1,1)
legend("topright", col = 1:7, legend = c("chi-sq","n=11","n=13","n=15","n=17","n=19","n=21"),lty=1,lwd =1.5)


```

## plots u'

```{r}
index = 3

# Defines the parameters of the plot
x.grid <- seq(0,120,length = 10000)
chisqcurve <- dchisq(x.grid, df = degfreed)

# Histogram of the distribution of u1 for one specific population size, overlapped by theoretical curve
par(pty="s")
hist(u1_distr_n[[index]], prob = TRUE, col = "white", ylim = c(0, max(chisqcurve)), breaks = 50);lines(x.grid, chisqcurve, col = 2, lwd = 2)
# Produces a Q-Q plot
theoretical_u1s <- qchisq(ppoints(length(u1_distr_n[[index]])), df = degfreed)
qqplot(theoretical_u1s,u1_distr_n[[index]]);abline(a= 0, b=1)
# use "xlim = c(0,40), ylim=c(0,40)" as arguents of "qqplot" to zoom into the tails of the qq plot

# Plot of the distribution of u1 approaching the chi-sq distribution as n increases
par(cex.axis=1.5,cex.lab =1.5)
plot(x.grid,chisqcurve, type = 'l', main = "", lwd = 2, xlab="U'", ylab="density",ylim = c(0,0.04), xlim = c(20,110))
for (i in 1:length(u1_distr_n)) {
  lines(density(u1_distr_n[[i]]),col = i+1, lwd = 2)
  #legend("topright", col = 1:7, legend = c("chi-sq","n=11","n=13","n=15","n=17","n=19","n=21"),lty=1,lwd =2)
}


# Plots the distance from the chi-sq distribution
u1_distance <- list()
for (i in 1:length(u1_distr_n)){
  u1_distance[[i]] <- sum(abs(quantile(density(u1_distr_n[[i]])$x,seq(0,0.99,0.01))-qchisq(seq(0,0.99,0.01),degfreed)))/100
}
plot(num_of_obs,u1_distance,type = "o",ylim=c(0,15000))

# Plots the value alpha as n increases
plot(num_of_obs,u1_alpha_n, type = "o");abline(h = 0.05)

```

## plots comparison
Comparison between the two distributions

```{r}
index = 1

par(cex.axis=1.5,cex.lab =1.5)
plot(num_of_obs,u1_distance,type = "o",main = "", xlab="n", ylab="distance",ylim=c(0,150),lwd =2)
lines(num_of_obs,u0_distance,type = "o",col = 'red',lwd =2);abline(h=0.05,lty=2)
#legend("topright", col = 1:2, legend = c("U'","U"),lty=1,lwd =2,cex=1.2)

plot(num_of_obs,u1_alpha_n,type = "o",ylim=c(0,1),main = "", xlab="n", ylab="alpha",lwd =2)
lines(num_of_obs,u0_alpha_n,type = "o",col = 'red',lwd =2);abline(h=0.05,lty=2)
#legend("topright", col = 1:2, legend = c("U'","U"),lty=1,lwd =2,cex=1.2)

plot(x.grid,chisqcurve, type = 'l')
lines(density(u1_distr_n[[index]]),col = 'red')
lines(density(u0_distr_n[[index]]),col = 'red')

plot(1,1)
legend("topright", col = 1:2, legend = c("U'","U"),lty=1,lwd =2,cex=1.2)
```


```{r}
par(mfrow=c(6,2))
par(oma=c(5,5,5,5))
par(mar=c(0.2,0.2,0.2,0.2))
par(mgp=c(2.5,1,0))

for (i in 1:6) {
  hist(u0_distr_n[[i]], prob = TRUE, col = "white",
     ylim = c(0, 0.05), xlim=c(10,110),
     breaks = 50, ylab = "", main = "", xlab = "",
     xaxt = "n", yaxt = "n")
  lines(x.grid, chisqcurve, col = 2, lwd = 2)
  hist(u1_distr_n[[i]], prob = TRUE, col = "white",
     ylim = c(0, 0.05), xlim=c(10,110),
     breaks = 50, ylab = "", main = "", xlab = "",
     xaxt = "n", yaxt = "n")
  lines(x.grid, chisqcurve, col = 2, lwd = 2)
}

mtext(paste(c('u', "u'")),at=c(0.3,0.8),side=3,outer=T,line = 1)
mtext(paste('n =',rev(num_of_obs)),at=seq(0.1,0.9,0.9/6),side=2,outer=T,line = 1)


```

```{r}
par(mfrow=c(6,2))
par(oma=c(0,5,1,1))
par(mar=c(3.2,4,1,1))
par(mgp=c(2.4,1,0))
#c(bottom, left, top, right)

for (i in 1:6) {
  hist(u0_distr_n[[i]], prob = TRUE, col = "white",
     ylim = c(0, 0.05), xlim=c(10,110),
     breaks = 50, ylab = "Density", main = "", xlab = "U")
  lines(x.grid, chisqcurve, col = 2, lwd = 2)
  hist(u1_distr_n[[i]], prob = TRUE, col = "white",
     ylim = c(0, 0.05), xlim=c(10,110),
     breaks = 50, ylab = "Density", main = "", xlab = "U'")
  lines(x.grid, chisqcurve, col = 2, lwd = 2)
}
mtext(paste('n =',rev(num_of_obs)),at=seq(0.1,1,1/6),side=2,outer=T,line = 1)


```


# Challenge 2: Power

## simulation chi-sq

```{r}
j=1
u0_power_rho_n <- list()
u1_power_rho_n <- list()

num_of_obs <- seq(from=11, to=100, by=10)
values_of_rho <- seq(from=-0.1, to=0.25, by=0.35/20)

for(N in num_of_obs) {
  nboot <- 10000 # Number of bootstraps
  alpha <- 0.05 # Significance level
  P <- 10 # Number of variables
  degfreed <- 1/2 * P * (P+1) -1
  
  u0_distr_rho <- list()
  u0_power_rho <- list()
  u1_distr_rho <- list()
  u1_power_rho <- list()
  
  k = 1
  
  quantile_u0 <- qchisq(1-alpha,degfreed)
  quantile_u1 <- qchisq(1-alpha,degfreed)

  
  for(rho in values_of_rho) {
    # Parameters for multivariate normal distribution, under a Compound Symmetry covariance structure
    mu <- rep(0,P) # Mean
    sigma <- matrix(rho,P,P) - (rho - 1) * diag(P) # Covariance matrix
    
    if(is.positive.definite(sigma)==TRUE) {
      u0_distr <- rep(0,nboot)
      u1_distr <- rep(0,nboot)

      
      for (i in 1:nboot) {
        mvn <- mvrnorm(N, mu = mu, Sigma = sigma ) # from MASS package
        u0_distr[i] <- u0(mvn)
        u1_distr[i] <- u1(mvn)

      }

      u0_distr_rho[[k]] <-  u0_distr
      u0_power_rho[[k]] <- (length(which(u0_distr_rho[[k]] > quantile_u0))) / length(u0_distr_rho[[k]])
      u1_distr_rho[[k]] <-  u1_distr
      u1_power_rho[[k]] <- (length(which(u1_distr_rho[[k]] > quantile_u1))) / length(u1_distr_rho[[k]])
      
    } else {
      u0_power_rho[[k]] <- 1
      u1_power_rho[[k]] <- 1

    }
  
    inc(k)
  }
  u0_power_rho_n[[j]] <- u0_power_rho
  u1_power_rho_n[[j]] <- u1_power_rho

  inc(j)
}


```

## simulation empirical

```{r}
j=1
u0_power_rho_n <- list()
u1_power_rho_n <- list()

num_of_obs <- seq(from=11, to=100, by=10)
values_of_rho <- seq(from=-0.1, to=0.25, by=0.35/20)

for(N in num_of_obs) {
  nboot <- 1000 # Number of bootstraps
  alpha <- 0.05 # Significance level
  P <- 10 # Number of variables
  degfreed <- 1/2 * P * (P+1) -1
  
  u0_distr_rho <- list()
  u0_power_rho <- list()
  u1_distr_rho <- list()
  u1_power_rho <- list()
  
  k = 1
  
  #under H0, finds quantiles for the distribution of u
  mu_h0 <- rep(0,P) # Mean
  sigma_h0 <- matrix(0,P,P)+ diag(P) # Covariance matrix
  u0_distr_underh0 <- rep(0,nboot)
  u1_distr_underh0 <- rep(0,nboot)
  for (i in 1:nboot) {
    mvn_h0 <- mvrnorm(N, mu = mu_h0, Sigma = sigma_h0)
    u0_distr_underh0[i] <- u0(mvn_h0)
    u1_distr_underh0[i] <- u1(mvn_h0)

  }
  quantile_u0 <- quantile(u0_distr_underh0, 1-alpha)
  quantile_u1 <- quantile(u1_distr_underh0, 1-alpha)


  for(rho in values_of_rho) {
    # Parameters for multivariate normal distribution, under a Compound Symmetry covariance structure
    mu <- rep(0,P) # Mean
    sigma <- matrix(rho,P,P) - (rho - 1) * diag(P) # Covariance matrix
    
    if(is.positive.definite(sigma)==TRUE) {
      u0_distr <- rep(0,nboot)
      u1_distr <- rep(0,nboot)

      
      for (i in 1:nboot) {
        mvn <- mvrnorm(N, mu = mu, Sigma = sigma ) # from MASS package
        u0_distr[i] <- u0(mvn)
        u1_distr[i] <- u1(mvn)

      }

      u0_distr_rho[[k]] <-  u0_distr
      u0_power_rho[[k]] <- (length(which(u0_distr_rho[[k]] > quantile_u0))) / length(u0_distr_rho[[k]])
      u1_distr_rho[[k]] <-  u1_distr
      u1_power_rho[[k]] <- (length(which(u1_distr_rho[[k]] > quantile_u1))) / length(u1_distr_rho[[k]])
      
    } else {
      u0_power_rho[[k]] <- 1
      u1_power_rho[[k]] <- 1

    }
  
    inc(k)
  }
  u0_power_rho_n[[j]] <- u0_power_rho
  u1_power_rho_n[[j]] <- u1_power_rho

  inc(j)
}


```



## plots u

```{r}
plot(values_of_rho,u0_power_rho_n[[1]], type = "l", xlim = c(-0.1,0.1),ylim = c(0,1),main = "Power curve of u as n increases", xlab="rho", ylab="power")
for(i in 2:length(u0_power_rho_n)-1){
  lines(values_of_rho,u0_power_rho_n[[i]], type = "l",col = i);abline(h = 0.05,lty=2)
  legend("bottomleft", col = 1:(length(u0_power_rho_n)-1), legend = c("n=11","n=21","n=31","n=41","n=51","n=61","n=71","n=81"),lty=1,cex = 0.8)
}
```

## plots u'

```{r}
plot(values_of_rho,u1_power_rho_n[[1]], type = "l", xlim = c(-0.1,0.1),ylim = c(0,1),main = "Power curve of u' as n increases", xlab="rho", ylab="power")
for(i in 2:length(u0_power_rho_n)-1){
  lines(values_of_rho,u1_power_rho_n[[i]], type = "l",col = i);abline(h = 0.05,lty=2)
  legend("topright", col = 1:(length(u1_power_rho_n)-1), legend = c("n=11","n=21","n=31","n=41","n=51","n=61","n=71","n=81"),lty=1,cex = 0.6)
}
```
## plots comparison

```{r}
par(mfrow=c(8,1))
par(oma=c(5,5,5,5))
par(mar=c(0.2,2,0.2,2))
par(mgp=c(2.5,0.1,0))

for (i in 1:8) {
  plot(values_of_rho,u1_power_rho_n[[i]], type = "l", xlim = c(-0.1,0.1),ylim = c(0,1),xaxt = "n")
  lines(values_of_rho,u0_power_rho_n[[i]], type = "l",col = 2);abline(h = 0.05, lty=2)
}
legend("bottomleft", col = 1:2, legend = c("u'","u"),lty=1,cex= 0.8)

#mtext(paste(c('u')),at=c(0.5),side=3,outer=T,line = 1)
mtext(paste('n =',rev(num_of_obs[1:8])),at=seq(0.05,0.95,1/8),side=2,outer=T,line = 1)



```


# Challenge 3: PCA investigation
PCA investigation

## simulation

```{r}
u0_power_rho_n_pca <- list()
u1_power_rho_n_pca <- list()


for (l in 1:4) {
  j=1
  u0_power_rho_n <- list()
  u1_power_rho_n <- list()

  
  num_of_obs <- seq(from=11, to=100, by=20)
  values_of_rho <- seq(from=0, to=0.4, by=0.4/15)
  
  for(N in num_of_obs) {
    nboot <- 5000 # Number of bootstraps
    alpha <- 0.05 # Significance level
    P <- 10 # Number of variables
    degfreed <- 1/2 * P * (P+1) -1
    u0_distr_rho <- list()
    u0_power_rho <- list()
    u1_distr_rho <- list()
    u1_power_rho <- list()

    k = 1
    for(rho in values_of_rho) {
      # Parameters for multivariate normal distribution, under a Compound Symmetry covariance structure
      mu <- rep(0,P) # Mean
      sigma <- matrix(rho,P,P) - (rho - 1) * diag(P) # Covariance matrix
      
      if(is.positive.definite(sigma)==TRUE) {
        u0_distr <- rep(0,nboot)
        u1_distr <- rep(0,nboot)


        for (i in 1:nboot) {
          mvn <- mvrnorm(N, mu = mu, Sigma = sigma ) # from MASS package
          mvn_pca <- prcomp(mvn)
          u0_distr[i] <- u0(mvn_pca$x[,1:(P+1-l)])
          u1_distr[i] <- u1(mvn_pca$x[,1:(P+1-l)])

        }
  
        u0_distr_rho[[k]] <-  u0_distr
        u1_distr_rho[[k]] <-  u1_distr

        u0_power_rho[[k]] <- (length(which(u0_distr_rho[[k]] > qchisq(1-alpha,1/2 * (P+1-l) * (P+1-l+1) -1)))) / length(u0_distr_rho[[k]])
        u1_power_rho[[k]] <- (length(which(u1_distr_rho[[k]] > qchisq(1-alpha,1/2 * (P+1-l) * (P+1-l+1) -1)))) / length(u1_distr_rho[[k]])
        
        
      } else {
        u0_power_rho[[k]] <- 1
        u1_power_rho[[k]] <- 1

      }
    
      inc(k)
    }
    u0_power_rho_n[[j]] <- u0_power_rho
    u1_power_rho_n[[j]] <- u1_power_rho

    inc(j)
  }
  
  u0_power_rho_n_pca[[l]] <- u0_power_rho_n
  u1_power_rho_n_pca[[l]] <- u1_power_rho_n
}
```

## plots u

```{r}
library(car)

q = 5

plot(values_of_rho,u0_power_rho_n_pca[[1]][[q]], type = "l", xlim = c(-0.1,0.3), ylim = c(0,1))
for(i in 2:length(u0_power_rho_n_pca)){
  lines(values_of_rho,u0_power_rho_n_pca[[i]][[q]], type = "l",col = i)
}

```

## plots u'


```{r}
library(car)

q = 5

plot(values_of_rho,u1_power_rho_n_pca[[1]][[q]], type = "l", xlim = c(-0.1,0.3), ylim = c(0,1))
for(i in 2:length(u1_power_rho_n_pca)){
  lines(values_of_rho,u1_power_rho_n_pca[[i]][[q]], type = "l",col = i)
}


```


## plots comparison

```{r}

par(mfrow=c(5,2))
par(oma=c(5,5,5,5))
par(mar=c(0.2,2,0.2,0.2))
par(mgp=c(2.5,1,0))

for (q in 1:5) {
    plot(values_of_rho,u0_power_rho_n_pca[[1]][[q]], type = "l", xlim = c(-0.1,0.3), ylim = c(0,1), ylab = "", xlab = "", xaxt = "n")
    for(i in 2:length(u0_power_rho_n_pca)){
      lines(values_of_rho,u0_power_rho_n_pca[[i]][[q]], type = "l",col = i)
    }
    plot(values_of_rho,u1_power_rho_n_pca[[1]][[q]], type = "l", xlim = c(-0.1,0.3), ylim = c(0,1), ylab = "", xlab = "", xaxt = "n", yaxt = "n")
    for(i in 2:length(u1_power_rho_n_pca)){
      lines(values_of_rho,u1_power_rho_n_pca[[i]][[q]], type = "l",col = i)
    }
}



mtext(paste(c('u', "u'")),at=c(0.25,0.75),side=3,outer=T,line = 1)
mtext(paste('n =',rev(num_of_obs)),at=seq(0.1,0.9,1/5),side=2,outer=T,line = 1)


plot(1,1)
legend("topright", col = 1:(length(u0_power_rho_n_pca)), legend = c("no variables removed","1 variable removed","2 variables removed","3 variables removed"),lty=1)

```